Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-09-30 paper/paper.tex
fix exp
start writing a related work section

@@

Concerning the feature computation block $B_1$, an important factor is the time support. When considering the commonly used duration of 25ms, the performance drop down to \ml{check value} $\%$. This demonstrates that the joint scattering is able to benefit from a larger time support, possibly to capture long term modulations which plays an important part when considering extended playing techniques.

>>>>

\section*{Related work}
Timbre involves multiple time scales in conjunction, from a few microseconds for an attack transient to several seconds for a sustained tone.
Therefore, computational models of timbre perception must summarize acoustic information over a long analysis window, typically amounting to $10^{4}$ digital audio samples or more.
Mapping this input to a feature space in which distances denote timbral dissimilarities requires a data-driven stage of dimensionality reduction.
The scientific literature exhibits a methodological divide as regards the collection of human-annotated data.

On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags'', encoded as binary outputs within some predefined label space.
Because such tags often belong to the publicly available metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music hosting platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.
Furthermore, supplementing user-generated content with the outcome of a crowdsourced annotation campaign  allows an explicit verification of instrument tags.
For instance, the Open-MIC dataset, maintained by the Community for Open and Sustainable Music Information Research (COSMIR), comprises a vast corpus of X polyphonic music recordings spanning X instruments, as a derivative of the Free Music Archive (FMA) dataset.
Another example is the Medley-solos-DB dataset, which comprises X monophonic excerpts from 8 instruments, as a derivative of the MedleyDB dataset of multitrack music.
Over the past decade, the surge of these large digital audio collections, together with the democratization of high-performance computing on dedicated hardware, has spurred the development of deep learning techniques, and notably deep convolutional networks, in music instrument recognition.
We refer to X for a recent review of the state of the art in this domain.

On the other hand, the field of music psychology investigates timbre with the aim of discovering its physiological and behavioral foundations.
In this setting, prior knowledge, however accurate, of instrumentation does not suffice to conduct a study.
Rather, each excerpt must be played back to multiple human listeners.
Yet, collecting subjective responses to acoustic stimuli is a tedious and unscalable procedure, thus restricting the size of the musical corpus under study.
Such restriction hampers the applicability of iterative representation learning algorithms, such as stochastic gradient descent in artificial neural networks.
Nevertheless, advanced methods in electrophysiology allow to observe the firing patterns of biological neurons in the presence of controlled stimuli.
This observation, originally carried out on the ferret, has led to a comprehensive mapping of the primary auditory cortex, in terms of its spectrotemporal receptive fields (STRF).

@@

Concerning the feature computation block $B_1$, an important factor is the time support. When considering the commonly used duration of 25ms, the performance drop down to $92\% \pm$. This demonstrates that the joint scattering is able to benefit from a larger time support, possibly to capture long term modulations which plays an important part when considering extended playing techniques.
